Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-07 paper/main.tex
cleaning todos

\todo[inline]{Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you also want
to have the ``visual part'' of the PPA then you need a visual paradigm}

@@

\todo[inline]{Der Schwung zu Sprache (wobei speech auch erst am Satzende kommt)
ist zu hart, da kommt man als Leser nicht gut mit}

@@

\todo[inline]{SE: focus on the events that are relevant to the analysis to
reduce complexity and explain these better}

\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
Ausführungen, wie welche Annotation dazu passt}

@@

\todo[inline]{mention low-level feature events for AV here as well}

@@

\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe jetzt
lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und AV?;
Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}

@@

\todo[inline]{Das mit den 8 kontrasten und 5 kontrasten habe ich nicht intuitiv
durchblickt. Was wurde da gegen was kontrastiert?}

@@

\todo[inline]{give reference to Neurovault.com}

\todo[inline]{- Bitte sauber differenzieren zwischen "Lokalisation der PPA" und
    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
Du oft das erste machst es aber als das zweite beschreibst}

\todo[inline]{Der vergleich mit VIS kommt bestenfalls en passant, VIS selber
wird gar nicht berichtet wäre aber wichtig zum andocken an die Literatur}

\todo[inline]{Es ist zwar hier nicht der Fokus, aber ich würde sehr darauf
wetten, dass Reviewer danach fragen: Wie sieht es im vergleich dazu mit Faces
aus?}

\todo[inline]{Figure 2 und 3: ich würde da wahrscheinlich weiter rein zoomen um
genauer den visuellen Kortex zu zeigen. Vor allem aber muss man sagen, dass bei
FFA/PPA etc eigentlich flatmaps bzw inflated brains, also surface-darstellungen
standard sind}

\todo[inline]{Die Anzahl der Überlappungen in Figure 3 ist schwer abzulesen,
hier lieber eine andere Farbskala (spectral sequence?) nutzen}

\todo[inline]{Das mit den cuts to new vs familar setting wird irgendwie nie so
richtig in den PPA kontext eingeordnet. Bzw. ich glaube ich bin verwirrt. Warum
ist das der hauptkontrast und nicht das viel näher liegende places vs faces?}

\todo[inline]{Noch etwas, das wahrscheinlich gefragt wird: Wie sehen die
Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen
regressoren bzw.  kategorien derselben (zumindest aber places vs faces) aus?}

\todo[inline]{Wenn ich mir Figure 4 anschaue, würde ich sagen, dass AO besser
die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}

\todo[inline]{Figure 5 ist irre kompliziert. Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia caspers)}

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.
% what we did
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used simplified stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from a visual localizer experiment.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.

@@

\todo[inline]{say why slice -11 was chosen}

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
corrected) can be found in the accompanying dataset.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (transversal slice z=-11 for all subjects).

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of audio-description's primary
        $t$-contrast (blue) that compares geometry-related nouns to non
        geometry-related nouns spoken by the audio-description's narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to new setting with cuts
        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects. Thus, the figure does not depict the
        left cluster of the AV stimulus in sub-09 and sub-18, and the right
        cluster of the AV stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=.8\linewidth]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right). The overlays depict voxels spatially
        contrained to be located in the temporal and occipital cortex (gray),
    PPA overlap of all subjects (blue), and individual PPA (red).}
    \label{fig:bland-altman} \end{figure*}

@@

\todo[inline]{Ich finde die result-synopsis noch nicht optimal. Vielleicht gehe
ich aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
"localizer vs naturalistic" im vordergrund stehen, AO vs AV dann eine sehr
spannende aber logisch nachgeschaltete Frage sein.}

\todo[inline]{Bei ergebnissen und Diskussionen zu Stability fehlt mir irgendwie
immer der Kontext, wie sich die kontraste denn unterschieden haben und welche
davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
wichtige Hinweise geben}

\todo[inline]{VIS vs AV vs AO: Wer liefert was über die PPA. Dieser Vergleich
bzw. die Diskussion über gemeinsamkeiten und unterschiede fehlt mir etwas}

\todo[inline]{RSC etc: Irgendwie waren die bis zu diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen}

>>>>

\todo[inline]{SE: Clou der ganzen Geschichte ist doch: Man braucht keinen
separaten Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you
also want to have the ``visual part'' of the PPA then you need a visual
paradigm}

@@

\todo[inline]{SE: Der Schwung zu Sprache (wobei speech auch erst am Satzende
kommt) ist zu hart, da kommt man als Leser nicht gut mit}

@@

\todo[inline]{SE: focus on the events that are relevant to the analysis to
reduce complexity and explain these better; COH: revised but maybe still not
``optimal''}

\todo[inline]{SE: wie gut passen die Annotationen zu den VIS Stimuli -> genauere
Ausführungen, wie welche Annotation dazu passt; COH: revised but maybe still not
``optimal''}

@@

\todo[inline]{mention low-level feature events for AV here as well and not just
in the figure caption}

@@

\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und
AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
bedeutet)}

@@

\todo[inline]{SE: Das mit den 8 kontrasten und 5 kontrasten habe ich nicht
intuitiv durchblickt. Was wurde da gegen was kontrastiert? COH: revised but
maybe still not optimal}

@@

\todo[inline]{SE: sauber differenzieren zwischen "Lokalisation der PPA" und
    "Antwortverhalten einer vorab definierten PPA". Ich habe den Eindruck, dass
Du oft das erste machst es aber als das zweite beschreibst}

\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur}

\todo[inline]{SE: würde wetten, dass Reviewer fragen: Wie sieht es im vergleich
dazu mit Faces aus?}

\todo[inline]{SE: Figures with group results: würde da wahrscheinlich weiter
rein zoomen, um genauer den visuellen Kortex zu zeigen; vor allem muss man
sagen: bei FFA/PPA etc sind flatmaps/inflated brains standard}

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen}

\todo[inline]{SE: cuts to new vs familar setting wird irgendwie nie so
richtig in den PPA kontext eingeordnet. Warum ist das Hauptkontrast und nicht
das viel näher liegende places vs faces? COH: should at least be clearer after
revision of method section}

\todo[inline]{SE: Wie sehen die Antworten innerhalb der "klassisch definierten" PPA für die verschiedenen regressoren bzw. kategorien derselben (zumindest aber places vs faces) aus?}

\todo[inline]{individual results: AO trifft besser die VIS-PPA "trifft" als AV. Das ist zumindest sehr überraschend, oder?}

\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia Caspers)}

% study goal
The goal of this study was to investigate if increased hemodynamic activity in
the PPA correlates with spatial information presented under more ecological
valid conditions.
% what we did
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used simplified stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from a visual localizer experiment.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary contrasts can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

@@

% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects.
% results in both subject and group space
Time series of all subjects were analyzed both in group space and subject space.
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps with Z>2.3, p<.05 cluster
corrected) can be found in the accompanying dataset.
% report here in group space
For better comparison of results across participants, we here report results
($z$-maps; Z>3.4, p<.05 cluster-corrected) of the analyses that was performed in
group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AO
and AV $t$-contrast, and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (transversal
slice z=-11 for all subjects was chosen as it depicts voxels of significant
clusters in almost all subjects).

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of audio-description's primary
        $t$-contrast (blue) that compares geometry-related nouns to non
        geometry-related nouns spoken by the audio-description's narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to new setting with cuts
        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the AV stimulus
        in sub-09 and sub-18, and voxels of right cluster of the AV stimulus in
        sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[scale=0.28]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right). The overlays depict voxels spatially
        contrained to be located in the temporal and occipital cortex (gray),
    PPA overlap of all subjects (blue), and individual PPA (red).}
    \label{fig:bland-altman} \end{figure*}

@@

\todo[inline]{SE: die result-synopsis noch nicht optimal. Vielleicht gehe ich
aber auch mit der falschen Perspektive ran? Für mich würde der Vergleich
"localizer vs naturalistic" im vordergrund stehen, AO vs AV dann eine sehr
spannende aber logisch nachgeschaltete Frage sein.}

\todo[inline]{SE: Bei Ergebnissen \& Diskussionen zu Stability fehlt mir
irgendwie immer der Kontext, wie sich die Kontraste denn unterschieden haben und
welche davon z.B. im Ergebnis wo von den anderen abgewichen haben. Das würde ja
wichtige Hinweise geben}

\todo[inline]{SE: VIS vs AV vs AO: Wer liefert was über die PPA. Dieser
Vergleich bzw. die Diskussion über Gemeinsamkeiten \& Unterschiede fehlt mir
etwas}

\todo[inline]{SE: RSC etc: Irgendwie waren die bis zu Diskussion eher ein
afterthought. Daher etwas überraschend, vielleicht in Einleitung und Results
schon mehr bringen}
